---
title: "Homework 6"
output: html_notebook
---

__Question 1:__ Choose a country (not the US). 

Use the package maps to show a map of the country:

```{r}
library(maps)
map(database = "world", regions = "Spain", exact = FALSE, boundary = TRUE, 
    interior = TRUE)
```

```{r}
map("world", "Spain")
map.cities(country = "Spain", capitals = 1)
```

The dataset `world.cities` included in the map package contain information about the location and population of several cities in the world. Create a new data frame containing only the cities in the country you chose:

```{r}
#newdf <- world.cities$country.etc == "Spain"
spain <- subset(world.cities, country.etc == "Spain")
spain

```

Now take a look the cities, choose a population threshold that will lead to only about 20 cities in your dataset and plot the location of these cities in the country map using the `map.cities` function :

```{r}
s2 <- subset(spain, pop > 214000)
#s2
map("world", "Spain")
map.cities(x = world.cities, country = "Spain", minpop = 214000, label = TRUE)
```

Now instead of using `map.cities`, create a new dataframe `myCities` with only the latitude and longitude of the cities you chose above. You are going to need to get this information directly from the `world.cities` dataset.

```{r}
myCities <- data.frame(s2$lat, s2$long)
myCities
```

Use the geosphere package to calculate the distances between each pair of cities (use the `distm` function). You will need to add row and column names to the result of `distm`.

```{r}
library(geosphere)
#distance matrix
distances <- distm(myCities, myCities, fun = distHaversine)
distances = distances/1000


distances = data.frame(distances, row.names = s2$name)
colnames(distances) <- rownames(distances)

distances
#not sure how to add header names.
```

Use this data frame to perform a PCoA, plot the results and compare to your original graph of the cities.

```{r}
library(ape)
newdist <- distances/1000
#newdist
pcoaRes <- pcoa(newdist)
pcoaRes

library(plotly)

pcoaResDf <- data.frame(pcoaRes$vectors)
pcoaResDf
#still working on it
```

```{r}
p <- plot_ly(pcoaResDf, x = ~Axis.1 , y = ~Axis.2, text = rownames(pcoaResDf), type = 'scatter',
             mode = "markers", marker = list(size = 11)) # width = 800, height = 600) #create a df from our PCoA results, get the vectors part of it and throw into pcoaResDf. The x and y should be columns of the dataframe. Text is the text shown with the points. type is scatter plot, mode could be line but we just want points because scatter plot
 
p <- layout(p, title = "PCoA from Spain City Distances", 
       xaxis = list(title = "PC 1", autorange='reversed'), #list of parameters to x axis
       yaxis = list(title = "PC 2", autorange='reversed'))
 
p
```